Machine Learning Clustering

Suppose you have an unlabelled set of observations$\{ x^{(1)},x^{(2)},x^{(3)},x^{(4)}, \ldots ,x^{(n)}\}$.
You run $k-$means with 50 random initializations and obtain 50 different clusterings solution of the data.
What is the recommended way of choosing which solution to use.

The Distortion Function
For each of the clustering solutions, the distortion function is computed as 
\[ \frac{1}{m} \sum^{m}_{i=1} \parallel x^{(i)} - \mu_c^{(i)}\parallel ^2 \]
The optimal clustering solution is the solution that minizes the distortion function.
Since a lower value for a distortion function, implies a better clustering, you should choose the clustering with 
smallest value of the distortion function.


%------------------------------------------------%

%ML Week 8

\subsection*{Finding Closest Centroids}

In the cluste assignment phase of the algorithm, the algorithm assigns every training example $x^{(n)}$ to the closest 
centroid, given the current position of the centroids.

\[ C^{(i)} := J \mbox{ that minimizes } \| x^{} - \mu_j \| ^2 \]

\begin{itemize}
\item $C^{(i)}$ index of the centroid clostest to $x^{(i)}$
\item $\mu_j$ is the position of the $j-$th centroid.
\end{itemize}

Computing Centroid Means

\[ 
\mu_k := \frac{1}{abs(C_k)} \sum_{i \in C_k} x^{(i)}
\]
%---------------%

A good way to initialize k-mean is to select $k$ distinct examples from the training set and set the cluster centroids equal to these selected examples.

On every iteration of $k-$means, the cost function $J(C^{(1)},C^{(2)},\ldots, C^{(n)},
\mu_1,\ldots \mu_k)$

The distortion function should either stay the same or decrease, in particular it should not increase.

%---------------%
Recommended Applications of PCA

\begin{itemize}
\item Data Compression: reducing the dimensionof input data $x^{(i)}$, which will be used in a supervised learning algorithm
(i.e. use PCA data so that your supervised learning algorithm runs faster.

\item Data Visualization: Reduce data to 2D ( or 3D) so that it can be plotted.
\end{itemize}
